Influence of School Closure on COVID-19 Contaminations in Ireland and Repercussions across Age Groups

### 2022-01-19 manuscript/manuscript.Rmd
upgrade figures

(ref:overall) Evolution of confirmed Covid-19 cases in Ireland alongside with school closures.
(ref:descriptive) Evolution of confirmed Covid-19 cases by age groups in Ireland: raw data (bars) and 7 day rolling average (lines).
(ref:gam) Standardized effect of the smooth term in Generalized Additive Model by age group.
(ref:te) Matrix of Transfer Entropy coefficient and their corresponding p-value according every age group combination. Age groups on the x-axis are influencing the age groups on the y-axis ($X \rightarrow Y$). * $p < .05$, ** $p < .01$, *** $p < .001$.

@@

df_school |>
  filter(schools_closed == 1) |>
  count(schools_closure_wave) |>
  rename(schools_closure_wave_n = n)

@@

df_school_long |>
  filter(schools_closure_day == 1 & age_group == "aged1to4") |>
  select(date, schools_closure_wave, schools_closure_wave_n)
```

@@

```{r overall, fig.width=4.5, fig.height=3, fig.cap="(ref:overall)", fig.pos = "!h"}
overall_plot <- df |> 
  ggplot(aes(date, total_cases)) +
  geom_tile(aes(fill = factor(schools_closed), height = Inf), na.rm = TRUE, alpha = .4) +
  geom_line(na.rm = TRUE) +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %y") +
  scale_fill_manual(labels = c("Open", "Closed", "Na"), values = c("light blue", "red", "orange")) +
  labs(
    x = "Date", 
    y = "Covid-19 Cases in Ireland",
    fill = "Schools"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    text = element_text(size = 10, family = "serif"),
    axis.text = element_text(size = 10),
    panel.background = element_rect(colour = "black", size = 0.1)
  )

@@

```{r descriptive, fig.width=4.5, fig.height=7, fig.cap="(ref:descriptive)"}
descriptive_plot <- df_long |> 
  ggplot() +
  geom_col(aes(date, covid_cases), na.rm = TRUE) +
  geom_line(aes(date, covid_cases_7davg, color = age_group), na.rm = TRUE) +
  scale_x_date("Date", date_breaks = "3 months", date_labels = "%b %y") +
  scale_y_continuous("Confirmed Covid-19 Cases in Ireland") +
  scale_color_manual(labels = age_name, values = age_color) +
  facet_grid(
    age_group ~ ., 
    scales = "free",
    labeller = as_labeller(
      c(
        aged1to4 = "1 to 4",
        aged5to14 = "5 to 14",
        aged15to24 = "15 to 24", 
        aged25to34 = "25 to 34", 
        aged35to44 = "35 to 44", 
        aged45to54 = "45 to 54", 
        aged55to64 = "55 to 64", 
        aged65to74 = "65 to 74", 
        aged75to84 = "75 to 84", 
        aged85up = "85 and up"
        )
      )
  ) +
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.placement = "outside",
    text = element_text(size = 10, family = "serif"),
    axis.text = element_text(size = 10),
    panel.background = element_rect(colour = "black", size = 0.1)
  )

@@

```{r te, fig.width=4.5, fig.height=4.5, fig.cap="(ref:te)"}
te_plot
```

@@

>>>>

(ref:overall) Evolution of confirmed Covid-19 cases in Ireland alongside with school closures periods in grey areas (SC).
(ref:descriptive) Evolution of confirmed Covid-19 cases by age groups in Ireland: raw data (bars) and 7 day rolling average (lines).
(ref:gam) Standardized effect of the smooth term in Generalized Additive Model by age group.
(ref:te) Matrix of Transfer Entropy coefficient and their corresponding p-value according every age group combination. Age groups on the x-axis are influencing the age groups on the y-axis ($X \rightarrow Y$). * $p < .05$, ** $p < .01$, *** $p < .001$.

@@

@@

df_school_closure <- df_school |> 
  filter(schools_closed == 1) |> 
  count(schools_closure_wave) |> 
  rename(schools_closure_wave_n = n) |> 
  right_join(df_school, by = "schools_closure_wave") |>
  filter(schools_closure_day == 1) |>
  select(schools_closure_start_date = date, schools_closure_wave, schools_closure_wave_n) |> 
  mutate(
    schools_closure_end_date = schools_closure_start_date + schools_closure_wave_n,
    schools_closure_name = glue::glue("SC {schools_closure_wave}"),
    x_text = schools_closure_start_date + (schools_closure_end_date - schools_closure_start_date)/2
    )
```

@@

```{r overall, fig.width=4.5, fig.height=3, fig.cap="(ref:overall)", fig.pos = "!h"}
overall_plot <-
  ggplot() +
  geom_rect(data = df_school_closure, aes(xmin = schools_closure_start_date, xmax = schools_closure_end_date, ymin = -Inf, ymax = Inf), alpha = 0.25) +
  geom_text(data = df_school_closure, aes(label = schools_closure_name, x = x_text, y = Inf), vjust = 2, family = "serif", fontface = "bold", size = 3) +
  geom_line(data = df, aes(date, total_cases), na.rm = TRUE) +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %y") +
  labs(
    x = "Date", 
    y = "Covid-19 Cases in Ireland",
    fill = "Schools"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    text = element_text(size = 10, family = "serif"),
    axis.text = element_text(size = 10),
    panel.background = element_rect(colour = "black", size = 0.1)
  )

@@

```{r descriptive, fig.width=4.5, fig.height=7, fig.cap="(ref:descriptive)"}
descriptive_plot <- df_long |> 
  ggplot() +
  geom_rect(data = df_school_closure, aes(xmin = schools_closure_start_date, xmax = schools_closure_end_date, ymin = -Inf, ymax = Inf), alpha = 0.25) +
  geom_col(aes(date, covid_cases), na.rm = TRUE) +
  geom_line(aes(date, covid_cases_7davg, color = age_group), na.rm = TRUE) +
  scale_x_date("Date", date_breaks = "3 months", date_labels = "%b %y") +
  scale_y_continuous("Confirmed Covid-19 Cases in Ireland") +
  scale_color_manual(labels = age_name, values = age_color) +
  facet_grid(
    age_group ~ ., 
    scales = "free",
    labeller = as_labeller(
      c(
        aged1to4 = "1 to 4",
        aged5to14 = "5 to 14",
        aged15to24 = "15 to 24", 
        aged25to34 = "25 to 34", 
        aged35to44 = "35 to 44", 
        aged45to54 = "45 to 54", 
        aged55to64 = "55 to 64", 
        aged65to74 = "65 to 74", 
        aged75to84 = "75 to 84", 
        aged85up = "85 and up"
        )
      )
  ) +
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.placement = "outside",
    text = element_text(size = 10, family = "serif"),
    axis.text = element_text(size = 10),
    panel.background = element_rect(colour = "black", size = 0.1)
  )

@@

@@

```{r te, fig.width=4.5, fig.height=4.5, fig.cap="(ref:te)", fig.pos = "!h"}
te_plot
```
